%%%%%%%%%%%%%%%%%
% This is an sample CV template created using altacv.cls
% (v1.6.5, 3 Nov 2022) written by LianTze Lim (liantze@gmail.com), based on the
% CV created by BusinessInsider at http://www.businessinsider.my/a-sample-resume-for-marissa-mayer-2016-7/?r=US&IR=T
%
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

%% Use the "normalphoto" option if you want a normal photo instead of cropped to a circle
% \documentclass[10pt,a4paper,normalphoto]{altacv}

\documentclass[10pt,a4paper,ragged2e,withhyper]{altacv}

%% AltaCV uses the fontawesome5 package.
%% See http://texdoc.net/pkg/fontawesome5 for full list of symbols.

% Change the page layout if you need to
\geometry{left=1.25cm,right=1.25cm,top=1.5cm,bottom=1.5cm,columnsep=1.2cm}

% The paracol package lets you typeset columns of text in parallel
\usepackage{paracol}


% Change the font if you want to, depending on whether
% you're using pdflatex or xelatex/lualatex
\ifxetexorluatex
  % If using xelatex or lualatex:
  \setmainfont{Lato}
\else
  % If using pdflatex:
  \usepackage[default]{lato}
\fi

% Change the colours if you want to
\definecolor{VividPurple}{HTML}{000000}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{2E2E2E}
% \colorlet{name}{black}
\colorlet{tagline}{VividPurple}
\colorlet{heading}{VividPurple}
\colorlet{headingrule}{VividPurple}
% \colorlet{subheading}{PastelRed}
\colorlet{accent}{VividPurple}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

% Change some fonts, if necessary
% \renewcommand{\namefont}{\Huge\rmfamily\bfseries}
% \renewcommand{\personalinfofont}{\footnotesize}
% \renewcommand{\cvsectionfont}{\LARGE\rmfamily\bfseries}
% \renewcommand{\cvsubsectionfont}{\large\bfseries}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

%% Use (and optionally edit if necessary) this .cfg if you
%% want to use an author-year reference style like APA(6)
%% for your publication list
% \input{pubs-authoryear.cfg}

%% Use (and optionally edit if necessary) this .cfg if you
%% want an originally numerical reference style like IEEE
%% for your publication list
\input{pubs-num.cfg}

%% sample.bib contains your publications
\addbibresource{sample.bib}

\begin{document}
\name{Matin Abbaspour}
\tagline{Android Developer}


\personalinfo{%
  % Not all of these are required!
  % You can add your own with \printinfo{symbol}{detail}
  \email{matinabbaspour@gmail.com}
  \phone{+98 915 738 9279}
  % \homepage{mabbaspour.ir}
  \linkedin{matinabbaspour}

}

\makecvheader

%% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
\AtBeginEnvironment{itemize}{\small}

%% Set the left/right column width ratio to 6:4.
\columnratio{0.6}

% Start a 2-column paracol. Both the left and right columns will automatically
% break across pages if things get too long.
\begin{paracol}{2}


\cvsection{Profile}
 {\normalsize\color{emphasis} Android Developer with 3+ years of experience designing, developing, testing, and maintaining Android applications in transportation, telemedicine, and e-shops projects.
 \par}
 \medskip
 
\cvsection{Experience}
\cvevent{Software Engineer}{\href{http://mobintabaran.ir}{Mobin Tabaran Intelligent Structures}}{Jul 2019 -- Jun 2022}{Mashhad, IRAN}

\divider

\cvproject {Bayan Player}
\begin{itemize}
\item Creating android streaming application (like Spotify and CastBox) that play synchronized audio files with text and images.
\item Developing a background service for playback.
\item Implementation of encryption for downloaded files.
\item Technologies Used - ExoPlayer, OrmLight, Android Services (Foreground
And Background), Broadcast Receiver, Lyric View
\end{itemize}

\divider

\cvproject{Car Management System}
\begin{itemize}
\item Get the driver's exact position and save the route traveled by the driver offline, and send it to the server when it becomes online.
\item Optimizing memory usage and improving performance by sending location data stored in DB as separate segments and processes.
\item Improving crash-free users up to 98\%.
\item Technologies Used - Android Location Manager, Map, SQLite, Google Fire-
base, Google Analytics, Alarm Manager
% \item Display suggested routes for one or more destinations.
% \item Routing and predicting the time of the mission.
\end{itemize}

\divider

\cvproject{\href{https://sspm.krec.ir/}{Maintenance System Of High Pressure Substations (HPS)}}
\begin{itemize}
\item Designing the UI and developing the application for Android tablets.
\item Technologies Used - Java, SQLite, Google ML Kit, Barcode Scanner, Download, And Upload Center
\end{itemize}


\cvsection{PROJECTS}

\cvevent{Android Developer And UI Designer}{\href{https://play.google.com/store/apps/details?id=ir.mumapp.patient}{MumApp}}{2022}{}
\begin{itemize}
\item Creating telemedicine application for receiving appointments and online visits for support and advice for mothers and daughters.
\item Including various questionnaires to measure mental and physical condition to help the doctor for diagnosis and treatment.
\item Blog content to improve knowledge and obtain updated information.
\item Online visit with the possibility of chatting and uploading photos and medical documents.
\item Technologies Used - Data Binding, View Binding, ViewModel, Material Design.
\end{itemize}


%% Switch to the right column. This will now automatically move to the second
%% page if the content is too long.
\switchcolumn
\cvsection{Personal Info}
\begin{itemize}
\item {Born In \textbf{August 24, 1999}}
\item {Live in
\href{https://www.google.com/maps/place/Mashhad,+Razavi+Khorasan+Province,+Iran/@36.2976014,59.5092469,12z/data=!3m1!4b1!4m5!3m4!1s0x3f6c911abe4131d7:0xc9c57e3a9318753b!8m2!3d36.2619922!4d59.6173096}
{\textbf{Mashhad}}}
\item {Marital Status: \textbf{Single} }
\item {Military Service: \textbf{Exempted from service}}
\end{itemize}


\cvsection{Education}
\cvevent{B.A Computer Software Engineering}{\href{http://mshdiau.ac.ir}{Islamic Azad University of Mashhad}}{ Sep 2017 -- Feb 2021}{}
\begin{itemize}
\item Passed 152 units with an average grade of 17.68 from 20.
\end{itemize}

\cvsection{Awards}
\cvevent{9Th Place (Honorary diploma)}{\href{https://skills.irantvto.ir/news/19result08/}{Mobile Applications Development}}{December 2021}{Iran - WorldSkills}
\begin{itemize}
\item Competition period is 3 consecutive days in the template of Hackaton with 18 participants.
\end{itemize}

\divider

\cvevent{Qualified Team}{\href{https://bit.ly/3Rsd13e}{Mobile Programming Marathon}}{November 2021}{Sharif University}
\begin{itemize}
\item Being among the top 10 teams in a competition of 58 teams.
\end{itemize}


\cvsection{SKILLS}
\begin{itemize}
\item Retrofit And OkHttp,  Restful API, ExoPlayer, Socket, OrmLight, Material Design.
\smallskip
\item Kotlin, Data Binding, View Binding, ViewModel, Live Data, Navigation component. Android Chart, Foreground Services, Background Services, Android Location Manager.
\smallskip
\item Firebase, Google Map, Google Analytics, Google ML Kit, Google Authentication, Google 
ARCore.
\smallskip
\item  Java Spring Boot, Thymeleaf, PostgreSQL.
\smallskip
\item .NET, SQL Server, LINQ, Razor.
\smallskip
\item  JavaScript, jQuery, Bootstrap.
\end{itemize}



\end{paracol}

\end{document}
